Transforming Trash as an Artistic Act

### 2015-11-10 chapter1.tex
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

%****************************************
% Structure of this chapter
% Section: topic and its significance
% Section: the purpose of this study
% Section: overview of chapters
% Section: a note on terminology

@@

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.
%

% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir?
% Meaning of words here. move reuse and recycle here.

% Belki direk bir sanat işiyle girebilirsin. Etkileyici olması açısından. Hangi iş olabilir? Çöpün ne olduğunu ele alan hem de ona karşı bir yaklaşım geliştiren bir örnek belki de benim işine çok benzeyen bir şey olabilir. Starbucks bardaklarından bir şeyler yapan insan olabilir.

% Amelie olabilir. Orada fotoğraf toplayan çocuk olabilir. Onları itinayla toplayan bir adam. Tren garındaki fotoğraf kulubesi. Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası. Bir birinden farklı bir sürü insan. Filmde neden böyle bir eyleme yer veriliyor? Film fotoğraflar üzerinden defter üzerinden ilerliyor. Onun çevresinden bir hikaye kurgulanıyor. İnsanların artıklarını topluyor. Bunlar baya baya aslında o insanlar. Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor. Çok iyi bir örnek mi bilmiyorum. Burada niyet nedir ki? Ben buna şöyle bir okuma getireceğim diyebilirim.

@@

WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles to giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that has no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.

Trash is global, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
% TODO look introduction of revista, there is a related reference above it.
\textbf{Trash is everywhere.}
% Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.

% Gene aslında sürekli tükettiği şeylerin fotoğrafını çken sanatçı.

% Intoductionua bir sanatçı fikriyle girip konuyu oradan açabilirim. Bir hikayesi yaklaşımı olabilir.

@@

% Background information about the thesis. Inspirational points. The fact of trash.

% Firstly as a part of art making. Changes in art making? // Sanatın köklerine inme abi. Sen sanat bağlamında anlatacaksın bunları. Zaten ilerisinde değineceğin şeyleri neden şimdi tekrardan anlatıyorsun.
In the beginning of the 20th century non-art objects enter the scope of art making. This is a revolutionary change in the making of art. Production of art and the approach to the art changed dramatically. This changes actually started at the end of the 19th century with impressionist. (But not related with non-art objects.) Picasso is the first artist that used non-art object in his works. Later many of them followed him. First works are collage and then collage.

@@

@@

Yes using non art objects in the art is introduced and opened new dimensions for the language of art. But some of them treated as sculptures from trash. Reflects our world. But it is not limited with this. It also evoke it. And offers an alternative.

% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash.

% Çöp hakkındaki genel geçer bilgileri sıralamak aslında iyi olabilir. Ya da bunun hakkındaki yanlış bilinmeyen şeyleri.

@@

% Çöpe dair araştırmalar falan.

% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti.

@@

@@

@@

% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili.

% Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.

%%%
%%%
%%% 
% Bu kısım aslında yukarda bahsedilen amacın nasıl yapılacağını anlatacak.
\section{Overview of Chapters}
Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash. The aim is (better) to understand the trash in cultural and theoretical aspects. (to better realization the notion of trash.)

Third chapter seeks the root of using trash in the artworks and looks through the sample artworks.

@@

@@

%****************************************
% Examples from other thesis.
% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology. // The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art). It is questioned the role of art in transformation of discarded items. This thesis follows the discussions of what is waste and the states of waste or meaning of waste. Within this thesis the project transformed the collected discarded items and then later spreads them to the community again. 
%........................................

@@

%****************************************
% Some comments
% This written portion was to evaluate the project in terms of a justificatory theoretical framework.
% This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.
% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda? 
% The project aims to what? and what needs to justify what it questions? 
% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.

@@

% Çöpün dönüşmesi diye bir şeyin olduğunu aslında kullanıcıya aktarmak gerekli introductionda.

@@

%****************************************
% JUSTIFICATION (Gerekçesi)
% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
% - Peki neden bu işi yapıyorsun. Alternatifi aramak. Değer bulmak, değer bulunabilceğine inanmam aslında. Belki de değer üretmek için o değerleri yıkmak gerekli. Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur. Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman. O yüzden çöpe atılması önemli. Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir. Çöplüğün bir başlangıç olması. Batırdığımız bitridiğimiz yerden yeni bir başlangıç. Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek. Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin. 
% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
% - Çöp bu sanat işlerinde dönüşmüştür. 
% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:

%****************************************
% ARGUMENTS:
% 
%........................................

%****************************************
% SANATTAKİ KÖKLERİ ÜZERİNE:
% picasso falan gibi adamların derdi sanata farklı objeleri sokarken ki amaçları ya da değerlendirildikleri nokta farklı bir şeyler yapmaları. O dönemki anlayışı yıkmaları. Onun yerine daha geniş bir alan imkanı sunmaları. Biz şu anda onların açtıkları alandan top koşturuyoruz bir nebze. Onların buna yaklaşımları ile bizimkiler arasındaki bazı farklılıklar olacak. En azından biz onların yıkları şeyi yıktığımız iddia edemeyiz. Çünkü o kalıplar, yaklaşımlar açıldı ve yeni bir üretim alanı insanlara sunulmuş oldu. Sorulacak yeni sorular, yapılacak yeni tartışmalar vardı. 
% Yani farklı dönemlerde farklı amaçlarla kullanılmıştır. Farklı şekillerde okumak mümkündür. Ama benim işime yarayanları seçmek gerekli bunları. Bir kısmı için bu sanatın diline yeni bir şey sokması, sanatın alanını genişletmesi, yeni tartışma alanları açması şekilde işime yarayacak. Diğerleri ise çöpe ele almaları 
%........................................

@@

%****************************************
% Reuse and Recycle
One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. If any item is used again and again over time, it is said to be reused. The main purpose of reusing is to lengthen the life of the item or material. We give out used clothes for charity which results in reusing. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. Why throw something away when you can give it another life? Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended

>>>>

%****************************************
% Structure of this chapter
% Section: explain the topic and its significance, raise curiosity, give same facts about it.
% Section: state the the purpose of this study, specify the focus of it.
% Section: overview of chapters and structure of thesis.
% Section: a note on terminology, clarification about the comprehensive terminology.

\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces. I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects. My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower. But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}

% Bence introductionda çöpün farklı şekillerde ele alınabileceğini bir şekilde göstermek gerekli. Burdaki genel geçer yaklaşımdan bahsetmek gerekli.

% Ele aldığımız çöp insanların çöpleri, günlük kullanımdaki çöpler. Çok da değerli olmayan yerine yenisi koyabileceğimiz çöpler.

In this thesis work to understand the different aspects of trash is a key element. Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here). Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

@@

In previous ages (pre industrial ages? which age?) objects and resources are used again and again. Production of objects are hard and laborious. \comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession (It is experienced by everybody.). During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

% FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
% TODO PRAP. REF.
\todo{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever. The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.}

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
% TODO PRAP. REF.
\paraphrase{We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can. The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.}

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.

% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir? 
% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash. 
People tend to think that trash is values because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless? They do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw away a It is stacked from another place. Value of objects are not static. Trash is not static also It has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash. The results are surprising. Trashes spread away across the country and this journey takes month. \todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo{consider Papua genen people}

% Cycle of trash
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

Even if people pay little attention, everybody do not. An artist takes photos of his every trash, like people take photos of their faces. He focuses on the thing that paid little attention, that is trash. At the end he exhibits all the photos by covering all the walls of room. It can seen as record of his activities, record of commodities. Most of them we are not aware of them. Draw the attention of is being thrown away and everytime and everywhere. They are too much and can only fit covering all the walls. \todo{artist}

Trash is global, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
% TODO look introduction of revista, there is a related reference above it.
\textbf{Trash is everywhere.}

% ARTWORK
% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuous

Why people are interested in rubbish. Some of the artist also interested in others trash. \comment{O çöplerde ne bulmayı umuyorlar ki? Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor. ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor. Bazen de olduğu gibi kullanıyorlar. bu açıdan önemli. Çöpü çöp şekliden sunan sanatçılar. Ama bu nasıl mümkün ki? fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar. Bence değil? bir şekilde müdahele var gene orada. o fotoğraflarda artık dikkatin objesi haline geliyor. çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.

% Amelie olabilir. Orada fotoğraf toplayan çocuk olabilir. Onları itinayla toplayan bir adam. Tren garındaki fotoğraf kulubesi. Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası. Bir birinden farklı bir sürü insan. Filmde neden böyle bir eyleme yer veriliyor? Film fotoğraflar üzerinden defter üzerinden ilerliyor. Onun çevresinden bir hikaye kurgulanıyor. İnsanların artıklarını topluyor. Onların değer vermedikleri şeyleri topluyor. Bunlar baya baya aslında o insanlar. Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor. Çok iyi bir örnek mi bilmiyorum. Burada niyet nedir ki? Ben buna şöyle bir okuma getireceğim diyebilirim. Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde. Bu arada bu fotoğraf toplama işi ilk değil. Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte. Ama benim işime yarayan kısmı ne? Neden o fotoğrafları ya da bunun filmini yapıyor. Aslında puzzlelar üretiyor. Belirli tekrar olacaktır. insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir. Tekrar bir kitap haline geliyor. Tanınmayan insanların fotoğrafları. Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon. Aslında tam da amelie bunu yapmıyor mu? Hikayeler üretiyor bu fotoğraflardan. Yeni karşılaşmalar üretmesi. Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır. Bin bir türlü şey vardır aralarında. Nereye yerleşmeli. Başkasının çöpünü toplama. O dönemin o eşyasını arşivini tutma. ve herkes sunuluyor sonrasında bu.

@@

WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that have no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks. There are mountains of trash and place is very limited. By squeezing them, WALL-E saves space. \todo{What is the context of it? Which part is related with my topic?} What are we going to do with all these mountains of trash? \todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.

@@

\todo{Background information about the thesis. Inspirational points. The fact of trash.}

% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti. 
\comment{In the beginning of the 20th century non-art objects enter the scope of art making. This is a revolutionary change in the making of art. Production of art and the approach to the art changed dramatically. This changes actually started at the end of the 19th century with impressionist. (But not related with non-art objects.) Picasso is the first artist that used non-art object in his works. Later many of them followed him. First works are collage which gluing different papers together. Yes using non art objects in the art is introduced and opened new dimensions for the language of art. But some of them treated as sculptures from trash. Reflects our world. But it is not limited with this. Some of the works are provokes the consumption habits of society and offers an alternative perception.}

@@

\comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on. However in this thesis study trash }

@@

@@

@@

This trash pheomanan catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Many type of it?

% Idea of everthing can be trash. Act of trashing. not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

@@

\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

@@

% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili. Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.

As many people are inside the business of transforming trash through craft and so on. People on the streets looking for aliminu cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them again the industry. In thesis they are not in the scope. People that give attention to the trash and behave artistic act is in the scope of this thesis.

% How does it become trash?
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Overview of Chapters}
This study is structured many examples of artworks in different part of the thesis. As the related topic or argument is presented example artwork is given at this moment. Immediately how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Art works are used as a supportive elements for the stated arguments. \comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.}

Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash. The aim is (better) to understand the trash in cultural and theoretical aspects. (to better realization the notion of trash.) It is explored the trash is being worked is whose trash. Or what type of society genarete this trash. Also in the project I collect the paper trash. What type of approach generate it and what are the dynamics of it? What type of trash we are talking about? It is understood through the patters of consumption patterns. And to reflect this cultural phenomena what phylosphers and scholars say. Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system. How explained the transient nature of trash?

\comment{First chapter will be about the conceptual framework that I have been working through
which includes historical and theoretical background.}

Third chapter seeks the root of using trash in the artworks and looks through the sample artworks. As already artworks are mentioned in the different part of the thesis, in this chapter focused on art (historical )

@@

\comment{The second chapter will consist of the overview of my work. I will start with the development process of the work. I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied. Development process of my work shaped the way I think on the subject of my thesis. Therefore, I will explain my process as detailed as possible. Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level. At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}

@@

@@

%****************************************
% Some comments
% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda? 
% The project aims to what? and what needs to justify what it questions? 
% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.

@@

@@

%****************************************
% JUSTIFICATION (Gerekçesi)
% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
% - Peki neden bu işi yapıyorsun. Alternatifi aramak. Değer bulmak, değer bulunabilceğine inanmam aslında. Belki de değer üretmek için o değerleri yıkmak gerekli. Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur. Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman. O yüzden çöpe atılması önemli. Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir. Çöplüğün bir başlangıç olması. Batırdığımız bitridiğimiz yerden yeni bir başlangıç. Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek. Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin. 
% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
% - Çöp bu sanat işlerinde dönüşmüştür. 
% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
%........................................

%****************************************
% SANATTAKİ KÖKLERİ ÜZERİNE:
% picasso falan gibi adamların derdi sanata farklı objeleri sokarken ki amaçları ya da değerlendirildikleri nokta farklı bir şeyler yapmaları. O dönemki anlayışı yıkmaları. Onun yerine daha geniş bir alan imkanı sunmaları. Biz şu anda onların açtıkları alandan top koşturuyoruz bir nebze. Onların buna yaklaşımları ile bizimkiler arasındaki bazı farklılıklar olacak. En azından biz onların yıkları şeyi yıktığımız iddia edemeyiz. Çünkü o kalıplar, yaklaşımlar açıldı ve yeni bir üretim alanı insanlara sunulmuş oldu. Sorulacak yeni sorular, yapılacak yeni tartışmalar vardı. 
% Yani farklı dönemlerde farklı amaçlarla kullanılmıştır. Farklı şekillerde okumak mümkündür. Ama benim işime yarayanları seçmek gerekli bunları. Bir kısmı için bu sanatın diline yeni bir şey sokması, sanatın alanını genişletmesi, yeni tartışma alanları açması şekilde işime yarayacak. Diğerleri ise çöpe ele almaları 
% Ben picassonun sahip olduğu kaygılarla sanat yapmıyorum. Yani ondan bahsetmek ya da sanatın bu işlerdeki köklerinden konuşmak benim için yeterli değil. DAha da fazlasına ihtiyacım var. 
% Benim kaygılarım ne peki? Ben kime hitap ediyorum, bence burada bir ayrım söz konusu.
%........................................

@@

%****************************************
% Reuse and Recycle
One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars \todo{ref}

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. If any item is used again and again over time, it is said to be reused. The main purpose of reusing is to lengthen the life of the item or material. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. Why throw something away when you can give it another life? Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

%****************************************
% UPCYCLING TERİMİNİ KULLANANLAR.
% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended
% Raw+Matrial=Art burda da upcycling deniliyor.
%........................................
